Generalized measurement invariance tests with application to factor analysis

### 2011-11-11 www/paper.Rnw
Fixed some broken citations in the paper and added to refs.bib.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@75 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Test statistics for the hypotheses \eqref{eq:exh0}
and~\eqref{eq:exh0.2} are displayed in Figure~\ref{cusumex}.
Each panel displays a test 
statistic's fluctuation across values of student GPA, with the first
column containing tests of~\eqref{eq:exh0} (testing $k*=4$ parameters)
and the second column containing tests of~\eqref{eq:exh0.2} (testing
$k*=1$ parameter).
The solid
horizontal 
lines represent critical values for $\alpha= 0.05$, and
the Cram\'{e}r-von Mises panels 
also contain a dashed line depicting the value of the test
statistic (test statistics for the others are simply 
the maxima of the processes).
In other words, for panels in the first and third rows, \eqref{eq:exh0} is
rejected if the process crosses the horizontal line.  For panels in
the second row, \eqref{eq:h0} is rejected if the dashed horizontal line is
higher than the solid horizontal line.

%% Details on test results
The results displayed in Figure~\ref{cusumex} generally show that the
``minority, stereotype prime'' group lacks invariance with respect to
GPA.  All three tests are significant at the .05 level when the four
group-specific parameters are tested simultaneously (first column).
When the intercept parameter is tested individually, two of the three
tests achieve significance (the CvM test and $\max \mathit{LM}$
statistics).  These results generally support the notion that domain
identification (as measured by GPA) influences the magnitude of
stereotype threat.  The $k*=1$ results also imply that the tests
differ in power and/or in error rates, an issue we address later in the
paper.

>>>>

Test statistics for the hypotheses \eqref{eq:exh0}
and~\eqref{eq:exh0.2} are displayed in Figure~\ref{fig:cusumex}.
Each panel displays a test 
statistic's fluctuation across values of student GPA, with the first
column containing tests of~\eqref{eq:exh0} (testing $k*=4$ parameters)
and the second column containing tests of~\eqref{eq:exh0.2} (testing
$k*=1$ parameter).
The solid
horizontal 
lines represent critical values for $\alpha= 0.05$, and
the Cram\'{e}r-von Mises panels 
also contain a dashed line depicting the value of the test
statistic (test statistics for the others are simply 
the maxima of the processes).
In other words, for panels in the first and third rows, \eqref{eq:exh0} is
rejected if the process crosses the horizontal line.  For panels in
the second row, \eqref{eq:h0} is rejected if the dashed horizontal line is
higher than the solid horizontal line.

%% Details on test results
The results displayed in Figure~\ref{fig:cusumex} generally show that the
``minority, stereotype prime'' group lacks invariance with respect to
GPA.  All three tests are significant at the .05 level when the four
group-specific parameters are tested simultaneously (first column).
When the intercept parameter is tested individually, two of the three
tests achieve significance (the CvM test and $\max \mathit{LM}$
statistics).  These results generally support the notion that domain
identification (as measured by GPA) influences the magnitude of
stereotype threat.  The $k*=1$ results also imply that the tests
differ in power and/or in error rates, an issue we address later in the
paper.
